### 2014-02-25 paper/retrofit.tex
Clean up theorem statement.

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \begin{equation} \label{eq:tsni-lhs}
    |its1| \approx_{|il|} |its2|
    \qquad \text{and} \qquad
    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
  \end{equation}
  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
  \begin{equation} \label{eq:tsni-rhs}
    |its1'| \approx_{|il|} |its2'|
     \qquad \text{and} \qquad
    |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
    \ \text{.}
  \end{equation}
\end{theorem}

\begin{lemma}
  \label{lemma:tsni}
  For any list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  |its1| \approx_{|il|} |its2|
  \qquad \text{and} \qquad
  |iconf iS1 its1| |.->| |iconf iS1' its1'|
  \end{equation}
  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  |its1'| \approx_{|il|} |its2'|
  \qquad \text{and} \qquad
  |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
  \ \text{.}
  \end{equation}
\end{lemma}

>>>>

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lhs}
    |ic1| \approx_{|il|} |ic2|
    \qquad \text{and} \qquad
    |ic1| |.->|^* |ic1'|
  \end{equation}
  then there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-rhs}
    |ic1'| \approx_{|il|} |ic2'|
     \qquad \text{and} \qquad
    |ic2| |.->|^* |ic2'|
    \ \text{.}
  \end{equation}
\end{theorem}

\begin{lemma}
  \label{lemma:tsni}
  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  |ic1| \approx_{|il|} |ic2|
  \qquad \text{and} \qquad
  |ic1| |.->| |ic1'|
  \end{equation}
  then there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2'|
  \ \text{.}
  \end{equation}
\end{lemma}
